### 2016-09-16 image_setup.tex
Today changes

\label{sec:image_setup}
In this section, we review the steps to create a common \ac{OS} image for
all the \ac{Raspi}s. The image setup is composed of three major steps:
Select and download the \ac{OS} image file, alter the image structure and
configure the \ac{OS} files. We proceed to detail all these steps providing
brief discussions to our setup choices when required. To perform these
steps, we indicate with command-line blocks the required sequential
commands to be typed by the testbed administrator in his / her \ac{PC}
to obtain the desired setting. In all the following sections, the number
sign (\#) and dollar sign (\$) will be used in the command blocks in the
paper to indicate if an operation needs to be run with root permissions or
common user permissions, respectively. The signs will be posted as the
terminal prompt in the command blocks.

>>>>

\label{sec:image_setup}
In this section, we review the steps to create a common \ac{OS} image for
all the \ac{Raspi}s. The image setup is composed of three major steps:
Select and download the \ac{OS} image file, alter the image structure and
configure the \ac{OS} files. We proceed to detail all these steps providing
brief discussions to our setup choices when required. To perform these
steps, we indicate with command-line blocks the required sequential
commands to be typed by the testbed administrator on his / her \ac{PC}
to obtain the desired setting. In all the command blocks in the paper, we indicate if a command needs to be run with root permissions (\#) or common user permissions (\$). These signs will prefix the commands.

### 2016-09-16 overview.tex
Today changes

We will refer to the
testbed administrator as the person(s) in charge of setting up and
configuring the testbed with administrator privileges from the \ac{OS}
point of view. The setting and configuration procedures are
performed by the testbed administrator in a \ac{PC} running a
Linux distribution as shown in Fig.~\ref{fig:testbed_setup}. Although in principle the administrator
Linux distribution is not a restriction, we present our procedure in a
Debian-based Linux distribution. Our basic design considers to create
a customized image to store it later on a memory card for each \ac{Raspi}.
Once configured, we store the resulting image file in a \ac{HTTP} server
as backup and in case the testbed administrator requires to make new
changes to this file. For our case, we use the university \ac{HTTP} server but any other servers can be used. We also put all the required configuration files
and scripts for the \ac{Raspi}s setup in the \ac{HTTP} server so there is
a single place where system setup is stored and could be modified.
This simplifies the system maintenance.
As
%another design consideration, when working on a testbed with many devices,
it may not always be desirable to make persistent changes
on the \ac{Raspi}s. For example when different users are interested in
running experiments on a rebooted testbed. We later present how
to utilize stacked filesystems to enable both persistent and
temporary storage to have this capability. Its purpose is to
remove non-desired data after a reboot while keeping the original
customized image structure. This step of the procedure is optional if
the testbed administrator decides to keep only persistent changes regardless
of the testbed use. Finally, we include a set of automation, monitoring
and cross-compilation tools over the top of our system in order to simplify
the execution of repetitive and long tasks, be able to follow the progress
of long task processes and compile relevant C++ source code for the testbed
administrator.

>>>>

We will refer to the
testbed administrator as the person(s) in charge of setting up and
configuring the testbed with administrator privileges from the \ac{OS}
point of view. The setting and configuration procedures are
performed by the testbed administrator in a \ac{PC} running a
Linux distribution as shown in Fig.~\ref{fig:testbed_setup}. Although in principle the administrator
Linux distribution is not a restriction, we present our procedure in a
Debian-based Linux distribution. Our basic design considers to create
a customized image to store it later on a memory card for each \ac{Raspi}.
Once configured, we store the resulting image file in a \ac{HTTP} server
as backup and in case the testbed administrator requires to make new
changes to this file. In our case, we use the university \ac{HTTP} server but
any others can be used. We also put all the required
configuration files and scripts for the \ac{Raspi}s setup in the \ac{HTTP}
server so there is a single place where system setup is stored and could be
modified. This simplifies the system maintenance.
As it may not always be desirable to make persistent changes
on the \ac{Raspi}s. For example when different users are interested in
running experiments on a rebooted testbed. We later present how
to utilize stacked filesystems to enable both persistent and
temporary storage to have this capability. Its purpose is to
remove non-desired data after a reboot while keeping the original
customized image structure. This step of the procedure is optional if
the testbed administrator decides to keep only persistent changes regardless
of the testbed use. Finally, we include a set of automation, monitoring
and cross-compilation tools over the top of our system in order to simplify
the execution of repetitive and long tasks, be able to follow the progress
of long task processes and compile relevant C++ source code for the testbed
administrator.
